Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
added roadmap

@@

\section{Heterosis in maize experiment}
\label{s:corn}

@@

\section{Discussion}
\label{s:discuss}

@@

>>>>

The remainder of the paper proceeds as follows. Section \ref{s:method} presents the proposed hierarchical model, an empirical Bayes method of estimating the parameters, and calculation of posterior probabilities of gene heterosis. Section \ref{s:simulation} presents a simulation study based on a maize experiment and compares our approach to alternative methods. Section \ref{s:maize} analyzes a maize experiment where phenotypic heterosis is well established and identifies genes demonstrating heterosis. The data and code necessary to perform this analysis is available in the Supplemental Material. Section \ref{s:discussion} summarizes the work and suggests directions for future research.

@@

\section{Heterosis in maize experiment}
\label{s:maize}

@@

\section{Discussion}
\label{s:discussion}

@@

Through a simulation study, we demonstarted that this method outperformed alternative methods (that are not designed to detect heterosis), and performed comparably with an implementation of our model in ShrinkBayes which estimates the full posterior via INLA.
